Memes: an R interface to the MEME Suite

### 2021-04-06 manuscript.Rmd
hard code table reference. Add note indicating import functions are made by me.

`memes` provides data import functions for each supported MEME Suite tool, which
import these data as modified R data.frames (described in detail below). These
functions can be called directly by users to import data previously generated by
the commandline or webserver versions of the MEME Suite for use in R. These
import functions also underlie the import step internal to each of the `run`
functions.

### structured data.frames hold multidimensional output data {-}

@@

Using this approach, the results can be visualized using  the
`view_tomtom_hits()` function to visually inspect the matches assigned by
TomTom, providing a simple way to assess the quality of the match.  A
representative plot of these data is shown in **Figure \@ref(fig:tomtom-example)**, while
the full results can be viewed in **Table \@ref(tab:tomtom-table)**. This analysis revealed
that the motifs associated with decreasing sites are highly similar to the E93
motif. Conversely, motifs found in increasing sites match the transcription
factors Br, L(3)neo38, Gl, and Lola (**Table \@ref(tab:tomtom-table)**). These data support
the hypothesis that E93 binding to its motif may play a larger role in chromatin
closing activity, while binding of the transcription factor br is associated
with chromatin opening.

>>>>

`memes` provides custom-built data import functions for each supported MEME
Suite tool, which import these data as modified R data.frames (described in
detail below). These functions can be called directly by users to import data
previously generated by the commandline or webserver versions of the MEME Suite
for use in R. These import functions also underlie the import step internal to
each of the `run` functions, ensuring consistent performance.

### Structured data.frames hold multidimensional output data {-}

@@

Using this approach, the results can be visualized using  the
`view_tomtom_hits()` function to visually inspect the matches assigned by
TomTom, providing a simple way to assess the quality of the match.  A
representative plot of these data is shown in **Figure \@ref(fig:tomtom-example)**, while
the full results can be viewed in **Table 1**. This analysis revealed
that the motifs associated with decreasing sites are highly similar to the E93
motif. Conversely, motifs found in increasing sites match the transcription
factors Br, L(3)neo38, Gl, and Lola (**Table 1**). These data support
the hypothesis that E93 binding to its motif may play a larger role in chromatin
closing activity, while binding of the transcription factor br is associated
with chromatin opening.
